XXX

### 2012-02-21 paper/engNERwiki.tex

\section{Related Work}
% Wikify! 
% Ide kell? Vagy Conclusion elé?

@@

Some sentences that were selected by the process above

@@

In this paper, we describe % not only ConLL

@@

>>>>

@@

There are many incomplete sentences in the Wikipedia text: image captions, enumerations items, contents of table cells, etc. On the one hand, these sentence fragments may prove to be of too low quality to be of any use in the traditional NER task. On the other hand, they could prove to be invaluable when training a named entity recognizer for user generated content. We have added a post-filtering step to recognize and label these fragments, so that users of the corpus can decide what to do with them. XXX

Manual inspection has found two conditions that can be used to detect fragments. A sentence is labelled as such if it either lacks a punctuation mark at the end or it contains no finite verbs. Our final corpus contains STAT full sentences and STAT fragments.
% TODO: Last sentence to evaluation? But then this whole subsection is too short.

@@

In this paper, we describe % not only ConLL? Do we need this?

@@

\section{Related Work}
% Wikify!
% stuff from Mining Meaning from Wikipedia
